

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{#2} \\
    \end{tabular*}
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{#3} & \textit{#4} \\
    \end{tabular*}
}

\newcommand{\resumeSubheadingSingleLine}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{#2} \\
    \end{tabular*}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Daniel Leboff}}\\
  \href{https://linkedin.com/in/danny-leboff}{LinkedIn: danny-leboff} & \href{mailto:}{danny.leboff@gmail.com} \\
  \href{https://github.com/Techatonic}{Github: github.com/Techatonic} & (+44)7920406639 \\
  \vspace{5pt}
\end{tabular*}
\\
{\large \textbf{Third year Computer Science undergraduate student at University of Cambridge.}}

\vspace{10pt}
%-----------EDUCATION-----------------
\section{\textbf{Education}}
  \resumeSubHeadingListStart
      \resumeSubheading
      {Trinity Hall, University of Cambridge}{2020-~~~~~~}
      {BA - Computer Science}{}
      {\small\newline{} Algorithms, Discrete Mathematics, Databases, Object-Oriented Programming, Machine Learning, Data Science, Semantics of Programming Languages, Compiler Construction, Logic and Proof, Artificial Intelligence, Formal Models of Language}
      \resumeSubheading
      {JFS School}{2018-2020}
      {A Levels}{}
      {\small
        \newline{} Mathematics A*, Further Mathematics A*, Physics A*, Computer Science A* 
        \newline{} British Mathematics Olympiad - Certificate of Distinction (2018)
        \newline{} Extended Project Qualification - An Evaluation of the P vs NP Problem (2019)
      }
      
      \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textit{GCSEs} & \textbf{2013-2018}\\
      \end{tabular*}
      {\small \newline{} 8 9s, 2 8s, 1 A*}
    \resumeSubHeadingListEnd
	    
\vspace{-5pt}
\section{\textbf{Skills}}
    \resumeSubHeadingListStart
	\resumeSubItem{Languages}{~~~~~~Python, Java, SQL, OCaml, TypeScript, C\#, Prolog}
	\resumeSubItem{Frameworks}{~~~~React Native, Unity3D}
	\resumeSubItem{Tools}{~~~~~~~~~~~~~~GIT, MySQL, MS SQL, REST API}
    \resumeSubHeadingListEnd
\vspace{-5pt}

\section{\textbf{Experience}}
  \resumeSubHeadingListStart
    \resumeSubheadingSingleLine{Softwire - Software Developer Intern}{Summer 2022}
    {\small Co-designed and developed a React Native application for a turtle conservation charity in Kenya. Created REST API endpoints on the backend for communication between client and server.}
    \resumeSubheadingSingleLine{Permutable Technologies - Data Science Intern}{Summer 2021}
    {\small Designed and developed an NLP algorithm to analyse and grade the sustainable nature of companies to aid prospective investors.}
    \resumeSubheadingSingleLine{Trinity Hall, University of Cambridge - JCR Webmaster}{2021-2022}
    {\small Enhanced and maintained the JCR website, resolved issues and ran the College's accommodation balloting system. Participated in regular meetings with senior College figures.}
    \resumeSubheadingSingleLine{Birkbeck, University of London - Work Experience}{2019}
    {\small Installed and upgraded computers and resolved software issues in the Systems Department.}
\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\vspace{-5pt}
\section{\textbf{Projects}}
\resumeSubHeadingListStart
\resumeItem{Killer Sudoku}
{Created an Android application to generate Killer Sudokus and ensure they have unique solutions using constraint satisfaction and backtracking. (2022) \\ Tech stack: Java, Prolog, Kotlin, Firebase}
\resumeSubItem{Safe-Building Competition}{Project-managed a team in a national safe-building competition, involving the design, documentation, development and testing, and presentation of a safe. (2019)}
\resumeSubItem{Unity3D Games}{Two android applications developed using Unity3D, released on the Google Play Store. (2016, 2018) \\ Tech stack: Unity3D, C\#, PHP, SQL}

\resumeSubHeadingListEnd
%--------Competitions--------------
\vspace{-5pt}
\section{\textbf{Competitions}}
\resumeSubHeadingListStart
    \item\small Hack Cambridge (2022) \vspace{-5pt}
    \item\small Reply Challenge (2019, 2020) \vspace{-5pt}
    \item\small Google CodeJam (2017, 2018, 2019) \vspace{-5pt}
    \item\small CodeChef Snackdown (2019) \vspace{-5pt}
    \item\small CodeFights Polyglot Marathon (2017)
\resumeSubHeadingListEnd
%---------Interests---------------
\section{\textbf{Interests}}
\small Rugby Fives (University team, Half-Blue), Pool (University team), Tennis (College captain), Football (College team), Rowing (College crew)
\end{document}